---
title: "Music Insights"
author: "Kaleb Crisci"
output: html_notebook
---

# We need to use Tidyverse for data import and manipulation
# If uninstalled, install with 'install.packages("tidyverse")'
```{r}
library(tidyverse)
```

# We need to use the Dplyr package to make the data tidyr
# If uninstalled, install with 'install.packages("tidyverse")'
```{r}
library(dplyr)
```

# Load in data
```{r}
survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")
```

# Cleaned up column Names
# Better to not use column number, because data can change and # future users inadvertently rename the wrong column
```{r}
colnames(survey)[colnames(survey) == "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "generator_name"

colnames(survey) <- c("time_submitted", "pseudonym_generator", "pseudonym", "sex", "academic_major", "academic_level", "year_born", "instrument_list", "favorite_song_artist", "favorite_song", "favorite_song_link")
```

## Create tables
# Person

```{r}
person <- tibble(time_submitted = survey$time_submitted, pseudonym = survey$pseudonym, pseudonym_generator = survey$pseudonym_generator, sex = survey$sex, year_born = survey$year_born, academic_level = survey$academic_level, academic_major = survey$academic_major)
```

# Song
```{r}
Favorite_song <- tibble(pseudonym = survey$pseudonym, favorite_song = survey$favorite_song, favorite_song_artist = survey$favorite_song_artist, favorite_song_link = survey$favorite_song_link, )

Favorite_song$pseudonym <- as.factor(Favorite_song$pseudonym)
```

# Parsed Dates
```{r}
person$time_submitted <- as.POSIXlt(parse_datetime(person$time_submitted, format="%m/%d/%y %H:%M"))
```

# Turn 2 columns into factors and combine extra factors together
```{r}
person$academic_major <- as.factor(person$academic_major)
person$academic_level <- as.factor(person$academic_level)
person$sex <- as.factor(person$sex)

levels(person$academic_major)[levels(person$academic_major) == "Computer information systems"] <- "Computer Information Systems"
```

#Create a Ratings table to clean the preferences table
```{r}
ratings <- gather(preferences, artist_songs, rating, "40 crew\tNot Enough":"Wheezer\tBuddy Holly")

colnames(ratings)[colnames(ratings)=="What was your pseudonym?"] <- "pseudonym"

ratings$artist_songs <- as.factor(ratings$artist_songs)
ratings$Timestamp <- as.POSIXct(parse_datetime(ratings$Timestamp, format="%m/%d/%y %H:%M"))

```

#Create ggplot of Ratings
```{r}
ggplot(ratings, aes(x = rating)) + geom_histogram(binwidth = 1)

```

#Create a box and whisker plot 
```{r}

ggplot(ratings, aes(y = rating, x = pseudonym)) + geom_boxplot()
```


This will create a table that shows how each individual rated their own favorite songs. It incorporates pattern matching. First, we create the new_table by joining the data from favorite_song and ratings by the column **pseudonym**. Once that is done, we filter out all the ratings for each pseudonym except the rating for their own favorite song. Notice how there are a few duplicates in the table with different ratings. We want to keep the duplicates that have the latest timestamp information. To do this, we must first order the data in the table by decreasing **Timestamp** and use the distinct() function on **pseudonym**. This will keep only the first occurrence of **pseudonym**, which will be the latest timestamp since it is now sorted in descending order. Finally, we use select() to pull out only the columns that we need.
```{r}

new_table <- inner_join(Favorite_song, ratings, by = "pseudonym") %>%
   filter(artist_songs != str_extract(artist_songs, favorite_song))
new_table <- new_table[order(new_table$Timestamp, decreasing = TRUE),] %>%
  distinct(pseudonym, .keep_all = TRUE) %>%
  select(pseudonym, favorite_song, rating)

summarize(new_table, mean(rating))

```

