---
title: "Music Insights"
author: "Kaleb Crisci"
output: html_notebook
---

# We need to use Tidyverse for data import and manipulation
# If uninstalled, install with 'install.packages("tidyverse")'
```{r}
library(tidyverse)
```

# We need to use the Dplyr package to make the data tidyr
# If uninstalled, install with 'install.packages("tidyverse")'
```{r}
library(dplyr)
```

# Load in data
```{r}
survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")
```

# Cleaned up column Names
# Better to not use column number, because data can change and # future users inadvertently rename the wrong column
```{r}
colnames(survey)[colnames(survey) == "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "generator_name"

colnames(survey) <- c("time_submitted", "pseudonym_generator", "pseudonym", "sex", "academic_major", "academic_level", "year_born", "instrument_list", "favorite_song_artist", "favorite_song", "favorite_song_link")
```

## Create tables
# Person

```{r}
person <- tibble(time_submitted = survey$time_submitted, pseudonym = survey$pseudonym, pseudonym_generator = survey$pseudonym_generator, sex = survey$sex, year_born = survey$year_born, academic_level = survey$academic_level, aademic_major = survey$academic_major)
```

# Song
```{r}
favorite_song <- tibble(pseudonym = survey$pseudonym, favorite_song = survey$favorite_song, favorite_song_artist = survey$favorite_song_artist, favorite_song_link = survey$favorite_song_link, )
```

